\documentclass{beamer}
\usetheme{Madrid}

\title{Project - Inventory Tracking System(ITS)} 
\author{P.Anudeep Rao \\ P.Rishi Manoj \\ J.Varshini}
\date{May 22, 2022}
\begin{document}


\begin{frame}
    \titlepage 
\end{frame}


\begin{frame}{Outline}
    \tableofcontents
\end{frame}

\section{Abstract}
\begin{frame}{Abstract}
    \begin{enumerate}[]
        \item This project is aimed at developing a desktop based application named Inventory Tracking System(ITS) for managing the details of inventory of a department in a college.
        \begin{itemize}
            \item Inventory Tracking System (ITS) is a tool that is used to manage/track the inventory of CSE Department.
        \end{itemize}
    \end{enumerate}
\end{frame}


\section{Field}
\begin{frame}{Field}
	\underline{\textbf{Field}}: \\
\begin{itemize}
\item These are the different areas/categories of places which a department comprises off.
\item The following are the types of fields:
\begin{itemize}
\item Lab
\item Class
\item Office
\item Library
\end{itemize} 
\end{itemize}
\end{frame}

\section{Object Classes}
\begin{frame}{Object Classes}
	\underline{\textbf{Object Class}}: \\
	\begin{itemize}
	\item An object class is the type of object in the field.
	\item ex: Boards, projector, benches etc.
	\end{itemize}
\end{frame}

\section{Object Instances}
\begin{frame}{Object Instances}
	\underline{\textbf{Object Instances}}: \\	
	\begin{itemize}
	\item The single entity of an object class is called as an object instance.
	\end{itemize}
\end{frame}

\section{Roles}
\begin{frame}{Roles}
\underline{\textbf{Roles}}:\\
\begin{itemize}
\item These are the positions of responsibilities which are needed to maintain the inventory.
\item The following are the types of roles:
\begin{itemize}
    \item Admin
    \item Operations Manager
    \item Supervisor
    \item Faculty
\end{itemize}
\end{itemize} 

\end{frame}

\section{Admin}

\section{Role - Admin}
\begin{frame}{Role - Admin}
    \begin{enumerate}[]
        \item Admin
        \begin{itemize}
            \item Admin appoints Operations Manager for each field.
            \item Verifying the info of the Operations Managers' and updating it to the database.
            \item He can access all the info of the inventory of the department.
            \item Admin provides the details of the sellers.
        \end{itemize}
    \end{enumerate}
\end{frame} 

\section{Role - Operations Manager}
\begin{frame}{Role - Operations Manager}
    \begin{enumerate}[]
        \item Operations Manager:
        \begin{itemize}
        \item Each field has a group or a single operations manager.
            \item OM has the power of creation and deletion the object classes for a field.
            \item OM appoints supervisor to a set of object classes or a single object class for maintaining the object classes.
            \item Verifying the info of the Supervisior and updating it to the database.
            \item OM can access all the info of the inventory of the field to which he is assigned to.
        \end{itemize}
    \end{enumerate}
\end{frame} 

\section{Role - Supervisor}
\begin{frame}{Role - Supervisor}
    \begin{enumerate}[]
        \item Supervisor:
        \begin{itemize}
            \item Supervisor adds or deletes a particular object instances.
            \item Supervisor can update the status of an object instance.
            \item Supervisor can access all the info of the inventory of the object classes which he was assigned for.
            \item The Supervisor is the person who buys the required product from the seller list provided by the Admin.
            \item Tracking of object instances is done based on an ID assigned to them.
        \end{itemize}
    \end{enumerate}
\end{frame}

\section{Role - Faculty}
\begin{frame}{Role - Faculty}
    \begin{enumerate}[]
        \item Faculty can access the info of inventory of Lab, Library and Classroom in view only mode.
    \end{enumerate}
\end{frame}

\section{Technical Details}
\begin{frame}{Technical Details}
\begin{itemize}
\item Frontend : JavaFX 
\item Backend : Java
\item Database : MySQL 
\item Tools used : Scene Builder, MySQL Workbench
\item IDE used : Intellej IDEA
\end{itemize}
\end{frame}

\section{Work Split}
\begin{frame}{Work Split in Project}
\begin{itemize}
\item Frontend : 
	\begin{itemize}
	\item Primary contribution : 1RishiManoj.P, Varshini.J
	\end{itemize}
\item Backend :
\begin{itemize}
\item Primary contribution : Anudeep Rao.P 
\item Helper : Varshini.J
\end{itemize}

\item Database : 
\begin{itemize}
\item Primary contribution : Anudeep Rao.P
\end{itemize}

\end{itemize}
\end{frame}

\begin{frame}{}
\begin{itemize}
\item For a more elaborated explanation of the project we request the reader to please look into the PDF's Frontend.pdf, Backend.pdf
\end{itemize}
\end{frame}



\end{document}
